Development of User-Friendly\\System Identification Techniques

### 2016-09-05 front-and-back-matter/acknowledgements.inc.tex
Fix typo in acks

The last person I would like to thank is my girlfriend Alexandra.
Without her encouragement, I am convinced I would never have finished my PhD.
I am grateful that you pushed me to not quit and that you did everything possible to bring this chapter in our lives to a good end, even though you yourself have also been void of concerns about your PhD.

>>>>

The last person I would like to thank is my girlfriend Alexandra.
Without her encouragement, I am convinced I would never have finished my PhD.
I am grateful that you pushed me to not quit and that you did everything possible to bring this chapter in our lives to a good end, even though you yourself have not been void of concerns about your PhD.
